---
title: "r4ds: strings"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---


To include a literal single or double quote within a string you can use \ to “escape” it:

double_quote <- "\"" # or '"'
single_quote <- '\'' # or "'"
That means if you want to include a literal backslash, you’ll need to double it up: "\\".


```{r}

writeLines(c("\"", "\\"))

```

`str_c` is equivalent to paste and paste0, except when NAs are involved str_c returns NA, and the paste functions convert NAs to string "NA" and continue the concat.

```{r}
paste("x", NA)
str_c("x", NA)
```



str_c works by multiplying the vectors and recylcing elements in the case one is a multiple of the other. The sep argument inserts a given string between every vector pair, while collapse further merges all pairs into one string and adds at the end of every pair a given string.
```{r}
x <- c("x", "g", "l")
y <- c("m", "n", "o")

str_c(x, y, sep="*", collapse = NULL)
```


14.2.5.3

If the string has an even number of characters, the middle character is considered to be the last character of the first half of the string.
```{r}
word <- "Samantha"

word1 <- "April"


middle_char <- function(string) {
  index <- str_length(string)-floor(str_length(string)/2)
  return(str_sub(string, index, index))
}

middle_char(word1)
```


```{r}
m <- "Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. "
```


```{r}
writeLines(str_wrap(m, width=40))
```


```{r}
?str_trim
```































