---
title: "r4ds: strings"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---


To include a literal single or double quote within a string you can use \ to “escape” it:

double_quote <- "\"" # or '"'
single_quote <- '\'' # or "'"
That means if you want to include a literal backslash, you’ll need to double it up: "\\".


```{r}

writeLines(c("\"", "\\"))

```

`str_c` is equivalent to paste and paste0, except when NAs are involved str_c returns NA, and the paste functions convert NAs to string "NA" and continue the concat.

```{r}
paste("x", NA)
str_c("x", NA)
```



str_c works by multiplying the vectors and recylcing elements in the case one is a multiple of the other. The sep argument inserts a given string between every vector pair, while collapse further merges all pairs into one string and adds at the end of every pair a given string.
```{r}
x <- c("x", "g", "l")
y <- c("m", "n", "o")

str_c(x, y, sep="*", collapse = NULL)
```


14.2.5.3

If the string has an even number of characters, the middle character is considered to be the last character of the first half of the string.
```{r}
word <- "Samantha"

word1 <- "April"


middle_char <- function(string) {
  index <- str_length(string)-floor(str_length(string)/2)
  return(str_sub(string, index, index))
}

middle_char(word1)
```


```{r}
m <- "Lorem Ipsum is simply dummy text of the printing and typesetting industry. Lorem Ipsum has been the industry's standard dummy text ever since the 1500s, when an unknown printer took a galley of type and scrambled it to make a type specimen book. "
```


```{r}
writeLines(str_wrap(m, width=40))
```


```{r}
v <- c()
v1 <- c("a")
v2 <- c("a", "b")
v3 <- c("a", "b", "c")
```


Function
```{r}

```




```{r}
string <- c("a", "b", "c")
```

```{r}

stringr168 <- function(string){
if (length(string) == 1) {
  return(string)
} else if (length(string) == 2) {
  return(paste(string[1], "and", string[[2]]))
} else if (length(string) >= 3) {
  end <- paste(string[length(string)-1], "and", string[[length(string)]])
  begin <- paste(string[[1:(length(string)-2)]], sep = ",")
  return(paste(begin, end, collapse=""))
}
}

```




```


REGEX

```{r}
x <- c("apple", "banana", "pear")

#start with 3 consonants
str_view(stringr::words, "^[^aeiou]{3}", TRUE)

#three or more vowels in a row
str_view(stringr::words, "[aeiou]{3,}", TRUE)


#two or more vowel-consonant pairs
str_view(stringr::words, "([aeiou][^aeiou]){2,}", TRUE)

```





```{r}

x <- c("+38970596321", "+38907056256")

str_view(x, "^\\+389\\d{8}", TRUE)
```


```{r}
x <- "\"\'\\"

writeLines(x)

str_view(x, "\"\'\\\\")

```



```{r}

? {0,1}

+ {1,}

* {0,}




```

1. Matches all strings, including empty ones.

2. Matches strings within curly braces, with one or more characters.

3. 4 digits followed by "-", then 2 digits, "-", and 2 digits again.

4. 4 literal slashes.




1. (.)\1\1 - any character appearing 3 times.
2. "(.)(.)\\2\\1" - it will match abba
3. (..)\1 - it will match abab
4. "(.).\\1.\\1" - matches any character followed by any character followed by twice the first character.
5. (.)(.)(.).*\\3\\2\\1 - matches anhy 3 characters followed by none or any number of characters, followed by the first 3 chracters in reverse order.

```{r}
#starts and ends with same character
str_view(stringr::words, "^(.).*\\1$", TRUE)

#starts and ends with same character pair
str_view(stringr::words, "^(..).*\\1$", TRUE)

#letter appears thrice
str_view(stringr::words, ".*(.).*\\1.*\\1.*", TRUE)
```










